Identifying Software Performance Changes Across Variants and Versions

### 2020-08-07 paper.tex
incorporated minor issues from reviewer 2

	\section{Evaluation}
	When evaluating our approach with a single experiment, we face a conflict between internal and external validity, a problem that is prevalent in software engineering research.~\cite{siegmund_views_2015}. 
	To become internally valid, the assessment of our approach with respect to accuracy requires prior knowledge of change points as ground truth, which is hardly obtainable as it would require exhaustive performance measurements across commits and configurations. Moreover, to assess aspects of external validity, such as scalability and sensitivity, we require a great degree of variation among subject system metrics (e.g., number of commits and options, domains of subject systems, etc.). 
	For a fair assessment, we require not only a large set of systems, but also the respective ground truth performance measurements. In brief, it is practically impossible to conduct such exhaustive performance measurements in the large, which is the main reason for proposing our approach in the first place.

>>>>

	\section{Evaluation}
	When evaluating our approach with a single experiment, we face a conflict between internal and external validity, a problem that is prevalent in software engineering research~\cite{siegmund_views_2015}. 
	To become internally valid, the assessment of our approach with respect to accuracy requires prior knowledge of change points as ground truth, which is hardly obtainable as it would require exhaustive performance measurements across commits and configurations. Moreover, to assess aspects of external validity, such as scalability and sensitivity, we require a great degree of variation among subject system metrics (e.g., number of commits and options, domains of subject systems, etc.). 
	For a fair assessment, we require not only a large set of systems, but also the respective ground truth performance measurements. In brief, it is practically impossible to conduct such exhaustive performance measurements in the large, which is the main reason for proposing our approach in the first place.
